### 2012-04-18 4.2.2.tex
chapters 2 and 4 have been swapped

% 4.2.2: Assessing models

\subsubsection{Basic correlations}
\subsubsection{Intramodal correlations}
\subsubsection{Residual correlations}

>>>>

\subsection{Computational models}

Applying these derived constraints to the lexicon increases saturation from 18.8\% to 28.8\% and incurs only a handful of exceptions. Yet, despite the fact that ``attestation'' is the minority pattern, attempts to identify static lexical constraints, whether by hand or computational model, lend little additional predictive power. There is no evidence that the English syllable contact inventory is subject to any static constraint at all. I am forced to conclude that most, if not all, of 71.2\% of possible clusters which are unattested are accidental gaps. Below, I show that this state of affairs follows directly from the sparse distribution of codas and onsets.

The three alternations targeting English syllable contact clusters have been shown to have the expected robust effects on the English lexicon.

Whereas the three alternations targeting English syllable contact clusters have robust lexical reflexes as measured by the Fisher exact test, such tests reveal no evidence for the static dispreferences identified by \citeauthor{Pierrehumbert1994}. There is now a growing literature on computational cognitive models of phonotactic learning. By applying these models to the syllable contact data, it is possible to exhaustively search for statistically motivated constraints, elimianting the possibility of human error.

To evaluate these statistical models, they are first trained on the set of attested clusters, then put to the task of classifying all possible clusters into those which are and are not attested. Four metrics are used to evaluate these computational models. Classification accuracy corresponds to the probability of a classification being either a true positive ($t.p.$), correctly predicting a cluster to occur, or a true negative ($t.n.$), correctly predicting a cluster to be absent. Incorrect outcomes are either false positives ($f.p.$), incorrectly predicting a cluster to occur, and false negatives ($f.n.$), incorrectly predicting a cluster to be absent.

%\ex Binary classification contingency table: \\
%\begin{tabular}{c | l l} \toprule
%                             & \multicolumn{2}{c}{prediction} \\
%\midrule
%\multirow{2}{*}{observation} & true positive ($tp$)  & false positive ($fp$) \\
%                             & false negative ($fn$) & true negative ($tn$) \\
%\end{tabular}
%\begin{tabular}{|l l|}
%\toprule
%true positive ($tp$)  & false positive ($fp$) \\
%false negative ($fn$) & true negative ($tn$) \\
%\bottomrule
%\end{tabular}
%\xe

\begin{example}
$\displaystyle \textrm{Accuracy} = \frac{t.p. + t.n.}{t.p. + t.n. + f.p. + f.n.}$
\end{example}

\noindent
A few other metrics can be used to assess classification performance. Precision corresponds to the probability that a cluster predicted to occur is observed in the data. 
\begin{example}
$\displaystyle \textrm{Precision} = \frac{t.p.}{t.p. + f.p.}$ 
\end{example}

\noindent
Recall (also known as sensitivity) is the probability a observed cluster is predicted to occur.

\begin{example}
$\displaystyle \textrm{Recall} = \frac{t.p.}{t.p. + f.n.}$
\end{example}

It is possible to maximize recall at the expense of precision, by predicting more clusters to be attested, or to increase precision at the expense of recall by predicting fewer clusters to be attested. A common way to balance these concerns is the $F_1$ score, which is the harmonic mean of precision and recall.

\begin{example}
$\displaystyle F_1 = 2 \left( \frac{\textrm{Precision} \times \textrm{Recall}}{\textrm{Precision} + \textrm{Recall}}\right)$ 
\end{example}

\subsubsection{Null baseline}

The 840 possible clusters have an 18.7\% of saturdaion rate. As a consequence of this sparsity, a null model which classifies all clusters as unattested achieves 81.3\% accuracy without the need to posit any constraints either derived or static. Since this model does not have any positive classifications, either true or false, precision, recall, and $F_1$ are undefined.

\subsubsection{Alternations}

As was shown above, \textsc{Obstruent Voice Assimiation}, \textsc{Coda Nasal Place Assimilation}, and \textsc{Degemination} are reliable predictors of what clusters are and are not attested and have few lexical exceptions. I generate another baseline by predicting only those clusters which do not violate any of these generalizations to be attested. This provides a significant improvement to the null baseline (accuracy = 0.857). As precision (0.401) is smaller than recall (0.708), there are more false positives (i.e., unattested clusters that do not violate any of these three alternation-derived generalizations) than there are false negatives (i.e., attested exceptions to these derived generalizations).

\subsubsection{\citet{Pierrehumbert1994}}

\citet{Pierrehumbert1994} first proposes to measure the well-formedness of syllable contact clusters by the independent probabilities of codas and onsets, and \citet{Coleman1997} extend this model to whole words. \citet{Pierrehumbert1994} uses both medial and initial/final codas and onsets to compute these probabilities, but I obtain a better fit to the data by only using medial coda and onset frequencies. Medial coda and onset probabilities are multipled to obtain a well-formedness score. This produces a continuous value between 0 and 1. To derive a binary classification from these values, I use a soft-margin support vector machine \citep{Cortes1995} with a linear kernel. This technique derives a ``decision stump'' providing the best single split into attested and an unattested clusters. This is not put forth as a cognitively plausible model for relating this expected probability to attestation: it is simply the upper bound that such a model could reach.

Unfortunately, this score only provides a small improvement to the null baseline
 (accuracy = 0.839), and has a lower accuracy and $F_1$ (0.328) than the alternation baseline.

\subsubsection{\citet{Hayes2008a}}

\citeauthor{Hayes2008a} develop a sophisticated method of learning phonotactic distributions from positive data. They develop software for estimating probability distributions over sequences of (sets of) phonological features using the principle of maximum entropy and making few assumptions about the independence of features. As above, a support vector machine with a linear kernel is used to turn these probability values into binary predictions. The software provided by these authors exposes many ``metaparameters'', operational decisions to be made in conducting an experiment with this system. To avoid any potential bias induced by the choice of these metaparameters, I use the same settings as used by \citet{Hayes2008a} in their similar study of English onset consonants. This includes the ``accuracy schedule'' [0.001, 0.01, 0.1, 0.2, 0.3] and no constraints on the number of constraints learned, as well English consonantal features used by \citeauthor{Hayes2008a}. Since this model is inherently stochastic, producing slightly different outcomes on each run, I follow the practice of \citeauthor{Hayes2008a} (p.~396) and report the lowest-accuracy of ten runs, though in general there is not a great deal of variation between individual runs.

This model provides a small improvement in accuracy (0.877) and $F_1$ (0.703) compared to the alternation baseline, but it has lower recall (0.642) than this baseline, indicating that the \citeauthor{Hayes2008a} model introduces many false negatives. 
%; it assigns the lowest probability value to 122 unattested clusters.
More specifically, it suggests that this model prefers narrower phonotactic generalizations than those derived from alternations. For instance, unattested *[m.kl] is assigned the highest probability, whereas it is ruled out by \textsc{Coda Nasal Place Assimilation}. On the other hand, the \citeauthor{Hayes2008a} model assigns a low score to clusters like those found in \emph{hu}[z.b]\emph{and} and \emph{pla}[t.f]\emph{orm}, though they are both attested and consistent with all three alternation-derived constraints.

\citet{Berent2012} identify an important defect with the \citeauthor{Hayes2008a} model used here: it does not make use of variables over features and thus fails to unify the constraint against geminate clusters. While the model may miss this unifying generalization, it correctly predicts all clusters containing geminates to be unattested.

The results for the four models are summarized below.

\begin{example}
Summary of computational model accuracy:

\vspace{0.5\baselineskip} 
\begin{tabular}{l | r r r r}
\toprule
                          & accuracy & precision & recall & $F_1$ \\ 
\midrule
Null baseline             & 0.813    & n.a.      & n.a.   & n.a.  \\
Alternations              & 0.857    & 0.401     & 0.708  & 0.512 \\
\citet{Pierrehumbert1994} & 0.839    & 0.210     & 0.750  & 0.328 \\
\citet{Hayes2008a}        & 0.877    & 0.777     & 0.642  & 0.703 \\
\bottomrule
\end{tabular}
\end{example}

One additional model was evaluated for this study. \citet{McGowan2011} claims that the type frequency of individual syllable contact clusters in English is predicted by the change of sonority in the clusters.\footnote{Thanks to Maria Gouskova for bringing this study to my attention.} Using a sonority scale proposed by \citet{Jespersen1904}, \citeauthor{McGowan2011} reports that clusters like [m.p], with sharply falling sonority, are slightly more frequent than those like [t.j], with rising sonority. However, \citeauthor{McGowan2011} finds that sonority of clusters accounts for only a tiny amount of the variance in cluster frequency ($R^2 = 0.077$). In this study, inclusion of sonority distance provided no improvement over the null baseline, and therefore was not considered further.

### 2012-04-18 4.2.3.tex
chapters 2 and 4 have been swapped

Above, we have seen that constraints on URs which are derive from phonological alternations restrict the contents of the lexicon. Applying these derived constraints to the lexicon increases saturation from 18.8\% to 28.8\% and incurs only a handful of exceptions. Yet, despite the fact that ``attestation'' is the minority pattern, attempts to identify static lexical constraints, whether by hand or computational model, lend little additional predictive power. There is no evidence that the English syllable contact inventory is subject to any static constraint at all. I am forced to conclude that most, if not all, of 71.2\% of possible clusters which are unattested are accidental gaps. Below, I show that this state of affairs follows directly from the sparse distribution of codas and onsets.

@@

\ex $\displaystyle Z_i = \frac{2 n_i}{r_{i + 1} - r_{i - 1}}$ \xe

@@

\ex $\displaystyle Z_1 = \frac{n_1}{r_2 - r_1}$ \xe
\ex $\displaystyle Z_N = \frac{n_N}{r_N - r_{N - 1}}$ \xe

@@

\ex $\displaystyle f(r; C, \alpha) = \frac{C}{r^\alpha}$ \xe

@@

\ex $\displaystyle \textrm{log}~Z_r \sim C + \alpha~\textrm{log}~r + \epsilon$ \xe

@@

That clusters (and the codas and onsets that make them up conforms to Zipf's law is not itself a deep observation. Zipfian distributions are characteristic of both syntactic rules \citep{Yang2009}, but also word \citep{Baroni2009} and phoneme \citep{Daland2011a} n-grams, and tokens in non-linguistic symbol systems \citep{Chomsky1958,Sproat2010} or randomly-generated texts \citep{Miller1957,Li1992}. The import of this statistical property for the study of cluster phonotactics is that it makes it difficult, on statistical grounds alone, to determine which unobserved events are excluded, and which are accidentally missing.

@@

\ex $\displaystyle \hat{p}_0 = \frac{n_1}{\sum N}$ \xe

@@

\ex {Simulation procedure}: \\
    \begin{tabular}{l l}
    a. & Sample a medial coda according to the observed probabilities  \\
    b. & Sample a medial onset according to the observed probabilities \\
    c. & Apply the SPE rules to the resulting cluster                  \\
    \end{tabular}
\xe

>>>>

Constraints on

Above, we have seen that constraints on URs which are derive from phonological alternations restrict the contents of the lexicon.

Applying these derived constraints to the lexicon increases saturation from 18.8\% to 28.8\% and incurs only a handful of exceptions. Yet, despite the fact that ``attestation'' is the minority pattern, attempts to identify static lexical constraints, whether by hand or computational model, lend little additional predictive power. There is no evidence that the English syllable contact inventory is subject to any static constraint at all. I am forced to conclude that most, if not all, of 71.2\% of possible clusters which are unattested are accidental gaps. Below, I show that this state of affairs follows directly from the sparse distribution of codas and onsets.

@@

\begin{example}
$\displaystyle Z_i = \frac{2 n_i}{r_{i + 1} - r_{i - 1}}$
\end{example}

@@

\begin{example}
$\displaystyle Z_1 = \frac{n_1}{r_2 - r_1}$
\end{example}

\begin{example}
$\displaystyle Z_N = \frac{n_N}{r_N - r_{N - 1}}$
\end{example}

@@

\begin{example}
$\displaystyle f(r; C, \alpha) = \frac{C}{r^\alpha}$ 
\end{example}

@@

\begin{example}
$\displaystyle \textrm{log}~Z_r \sim C + \alpha~\textrm{log}~r + \epsilon$ 
\end{example}

@@

That clusters (and the codas and onsets that make them up conforms to Zipf's law is not itself a deep observation. Zipfian distributions are characteristic of both syntactic rules \citep{Yang2009}, but also word \citep{Teahan1998,Ha2002,Baroni2009} and phoneme \citep{Daland2011a} n-grams, and tokens in non-linguistic symbol systems \citep{Chomsky1958,Sproat2010} or randomly-generated texts \citep{Miller1957,Li1992}. The import of this statistical property for the study of cluster phonotactics is that it makes it difficult, on statistical grounds alone, to determine which unobserved events are excluded, and which are accidentally missing.

@@

\begin{example}
$\displaystyle \hat{p}_0 = \frac{n_1}{\sum N}$ 
\end{example}

@@

\begin{example}
Simulation procedure: \\
    \begin{tabular}{l l}
    a. & Sample a medial coda according to the observed probabilities  \\
    b. & Sample a medial onset according to the observed probabilities \\
    c. & Apply the SPE rules to the resulting cluster                  \\
    \end{tabular}
\end{example}

### 2012-04-18 4.3.tex
chapters 2 and 4 have been swapped

% 4.3: Conclusion

It is not the case that this evidence is inconsistent with the hypothesis that there are additional degrees of wordlikeness: it is just a demonstration that these data to not require it.

>>>>

\section{Conclusions}

\citet{Borowsky1989} on peripherality.

productive \citet{Duanmu2008}

The above is a stark reminder.

A reasonable objection to the arguments presented in this chapter is to view the results as little more than an indictment of the results of \citealt{Pierrehumbert1994}.

However, the fact that state-of-the-art models are not capable of providing large improvements to the predictive accuracy indicates

 do not have a statistically significant effect on the shape of the English lexicon, but that experiments might turn up evidence that speakers have internalized

shown to be aware of static constraints if they reached statistical significance.

 statistically reliable static constraints could be identified

The of

Regarding the historical developments,

\citet{Martin2007}

On the other hand, patterns created by sound change are not guaranteed to persist over time. 
One example of non-persistence is discussed by \citet{Iverson2005}.  
Around 1100 CE, Old English \emph{sk} became [ʃ]. 
This sound change introduced no alternations.
Since long vowels were not found before tautosyllabic syllable clusters at this time, there were no \emph{V\lm sk\#} words when the
 change was actuated, and \emph{V\lm sh\#} continues to be rare in Modern English. 
What \citeauthor{Iverson2005} observe, however, is that there is nothing apparently peripheral about words like \emph{leash} or \emph{whoosh}, and loanwords and coinages have readily filled the gap.

A third pattern is that a historically inherited pattern

\citet[][140]{Frisch2004} suggest that the strong tendency for the first and second consonants of the Arabic root to be non-identic
al is the ``a diachronic result of a processing constraint that disfavors repetition.'' 
Unfortunately, there is no evidence that this pattern is diachronic other than in the sense that it appears to be inherited from the proto-language: there is simply no Proto-Semitic verb roots with identical first and second consonants \citep[][178]{Greenberg1950}. 
In other Semitic languages, the inherited patern has experienced considerable erosion.

\begin{example}
Tigrinya roots with identical first and second consonants \citep{Buckley1990a}: \\
\begin{tabular}{l l l l}
a. & lʌlʌw     & `scorch'                   & (< Ge'ez \emph{lʌwlʌw} `inflame')     \\
   & mʌmʌy     & `winnow'                   & (< Ge'ez \emph{mʌymʌy} `distinguish') \\
%   & mʌmʌt & `pick out loot' & (< 
b. & s’ʌs’ʌw   & `finish off a drink'       & (cf. \emph{s’ʌws’ʌw} `gulp down')           \\
   & t’ʌt’ʌf   & `prune tree'               & (cf. \emph{t’ʌft’ʌf} `smear wall with mud') \\
c. & kʷakʷkʷʌr & `waste away, be emaciated' & (cf. \emph{kʷarkʷʌr} `interrogate')         \\
   & kakʷkʷɨʕ  & `clean wax from ears'      & (cf. \emph{kaʕkʷɨʕ} `start to form pods')   \\
\end{tabular}
\end{example}

Similar exceptions are found in 
%Amharic (\citealp[][?]{Broselow1984}, \citealp[][?]{McCarthy1985}) and 
Hebrew \citep[][29]{Bat-El2005}.

The next two chapters return to the question of synchrony, addressing the relationship between statistical patterns in the lexicon and speakers' behaviors when presented with underrepresented sequences.

accidental gaps
\citet[][419f.]{Hayes2008a}

### 2012-04-18 4.tex
chapters 2 and 4 have been swapped

% 4: Gradient and categorical aspects of wordlikeness judgements

(though few if any phonologists regard $n$-gram segment probabilities as a core component of phonology)

\begin{quotation}
``...the greatest defect of classical philosophy of the mind...seems to me to be its unquestioned assumption that the properties and content of the mind are accessible to introspection.'' \citep[][22]{Chomsky1968}
\end{quotation}

>>>>

\chapter{Accidental and structural gaps in English syllable contact}
\label{clusters}

The term \emph{lexicon} has many senses: throughout, I use it to refer simply to the set of underlying representations.
%\citep[][269]{LANGUAGE}.

In the preceding chapter, it was proposed that

Reconsider the null hypothesis presented in the preceding chapter:

\begin{example}
The null hypothesis: \\
Universal grammar does not countenance constraints on the contents of URs
\end{example}

The idea

relationship to proposal

One primary way which this null hypothesis has been critiqued is by demonstrating that the lexicon of some language 
exhibits dispreferences or gaps corresponding to.

argue by trends in the lexicon

possibility of sparsity (C\&H, Fischer/Vogt and recent stats)

Of course, to obtain the desired results, we must guarantee that each sequence structure rule reflects a general systematic fact about the language, and not a fact which is due merely to the existence of accidental gaps in the lexicon. \citep[][401, fn.~8]{Stanley1967}

In the preceding chapter, it was proposed that

Lexicon

This appears to be exceptionlessly true of Arabic

That even gradient patterns

One of the first study of this type was an analysis of co-occurrence restrictions on consonants in Javanese roots by \citet{Mester1988}, recently revisited by \citet{Graff2011}. 
Another Austronesian language studied in this fashion is Muna \citep{Coetzee2008a,Anttila2008}.
This technique has been applied to consonants in Semitic, especially Arabic \citep{McCarthy1988,McCarthy1994,Pierrehumbert1993,Frisch1996,Frisch2004,Coetzee2008a} but also in Tigrinya \citep{Buckley1997}, Hebrew \citep{Berent2003}, and Amharic \citep{Colavin2010}, and to various co-occurrence restrictions in English \citep{Berkley1994b,Berkley1994a,Pierrehumbert1994,Dmitrieva2008a,Dmitrieva2008b,Coetzee2008b}, Russian \citep{Padgett1992}, Dutch \citep{Graff2011}, Navajo \citep{Martin2007,Martin2011} and Gitksan \citep{Brown2010}.

The absence of 
The claim here is that however stark the absence or underrepresentation of some form is, it

This hypothesis admits the possibility that there may be accidental gaps in the lexicon, a possibility which predates generative thinking:

\begin{quotation}
\ldots the fact that some [clusters--KG] are not found must be due to accidental gaps in the inventory of signs, and cannot be explained by structural laws of the language. \citep[][16]{Fischer-Jorgensen1952}
\end{quotation}

\noindent
Hans \citeauthor{Vogt1954} makes a similar observation in his study of Georgian clusters

\begin{quotation}
Although my material is drawn from a fairly extensive corpus---all accessible dictionaries and vocabularies, printed texts of tens of thousands of pages as well as ordinary speech---there is every reason to believe, as experience has shown, that additional material would yield new clusters. The material will never be complete. It will always contain accidental gaps \ldots partly because some clusters by pure chance do not occur in the vocabulary. \citep[][30]{Vogt1954}
\end{quotation}

\citet{Chomsky1965}

This chaper demonstrates that apparently systematic gaps may arise even in the absence of phonotactic preferences, and that this possibility compromises attempts to show that such preferences shape the lexicon.

\input{4.1}
\input{4.2}
\input{4.3}

### 2012-04-18 7.1.2.tex
More arranging.
chapters 2 and 4 have been swapped

\footnote{Thanks to Toni Cook for bringing this example to my attention.}

@@

\ex Linear structure of the Kinande infinitive: \\
\begin{tabular}{l l l l l l l}
e- & -rí- & -bí & tum & -ir & -an & -a \\
\{\textsc{Aug} & \textsc{Pre} & \texsc{OM}\} & \{send & \textsc{Appl} & \textsc{FV}\} \\
\multicolumn{7}{l}{``to send them to each other''}
\xe

>>>>

\footnote{Thanks to Toni Cook for bringing this study to my attention.}

@@

\ex Linear structure of the Kinande infinitive: \\
\begin{tabular}{l l l l l l l}
e- & -rí- & -bí & tum & -ir & -an & -a \\
\{\textsc{Aug} & \textsc{Pre} & \textsc{OM}\} & $\surd$\textsc{send} & \textsc{Appl} & \textsc{FV}\} \\
\multicolumn{7}{l}{``to send them to each other''}
\end{tabular}
\xe

### 2012-04-18 pre.tex
Went all Unicode, all the time.
Restructured into smaller files, wrote much of chapter 2.
Drastic restructuring and some writing on chapters 2-3.
chapters 2 and 4 have been swapped

\section{``What is the most important fact?''}

@@

This

>>>>

@@

In this dissertation, I critique two such epicyclic proposals, and present solutions using independently-motivated grammatical machinery to account for the data.

The first half of this dissertation began with a suggestion from Charles Yang that the sparse nature of the lexicon might itself account for at least some phonotactic gaps. The success of the resulting study, in chapter four, led me to question the received wisdom that speakers' knowledge of phonotactic generalizations is gradient and potentially independent of the phonological system.

These results support a null hypothesis in which phonotactic knowledge is derivative of the language acquisition device and phonological processes. While I present this theory as a falsifiable scientific hypothesis, an alternative would treat this proposal as a \emph{negative heuristic}, a

guides us away from ``phonotactic grammar'' as an explanatory device.

even those who are not inclined to accept this proposal should note how much of the coverage traditionally attributed to

can be accounted for by the nu

The second half of the dissertation develops a theory of inflectional gaps. I was pleased to hear (from Greville Corbett) that Stephen Anderson regarded inflectional gaps as ``the biggest scandal in morphology'', and even more so when Prof. Anderson agreed to serve as the external member of my committee.

In developing this theory, I have focused primarily on how inflectional gaps could be learned, and thus my approach is does not directly bear on competing morphological theories. At the same time, this theory is consistent with a proposal by \citet{Pesetsky1977} that inflectional gaps provide novel evidence for the ordering of various components of morphology. As an example, consider a few Russian verbs exhibiting inflectional gaps in the 1sg non-past.

\ex Russian 1sg. imperfect gaps \citep[after][]{Pesetsky1977}: \\
\begin{tabular}{l l l@{}l@{}l@{}l@{}l@{} l}
   & infinitive &   & 1sg. non-past \\
a. & pobedit{j} & * & pobeʒu  & / & * & pobeʒdu  & `conquer'   \\
   & ubedit{j}  & * & ubeʒu   & / & * & ubeʒdu   & `persuade'  \\
b. & tʃudit{j}  & * & tʃuʒu   & / & * & tʃuʒdu & `act oddly'   \\
   & otʃudit{j} & * & natʃuʒu & / & * & natʃuʒdu & `alienate'  \\
\end{tabular}

\noindent
As \citealt{Pesetsky1977} notes, the ill-formedness of the 1sg. non-past forms is shared by verbs related by prefixation. The opposite pattern can be seen in English.

\ex English preterite gaps: \\
\begin{tabular}{l l l@{}l@{}l@{}l@{}l@{}}
   & present  &   & preterite &   &   &           \\
a. & foresee  &   & foresaw   &   &   &           \\
   & sightsee & * & sightsaw  & / & * & sightseed \\
b. & undergo  &   & underwent &   &   &           \\
   & forgo    & * & forwent   & / & * & forgoed   \\
\end{tabular}

Unlike the pattern observed in Russian, verbs that appear to share the same root do not show the same patterns of defectivity. If we simply label the process of verbal inflection as the source of inflectional gaps, we can understand this contrast as follows: in Russian, inflection precedes and feeds prefixation; in English, the formation of complex verb stems and feeds the inflectional system.

While at this time I do not have any insights derived from these facts, there exists a potential to use inflectional gaps for evidence of ordered operations in morphology. These inferences are available to any account that recognizes inflectional gaps as something about the inflectional system, including the one presented here, but not if inflectional gaps are due to phonological properties of the derived objects.

The two parts of this dissertation were conceived and executed separately, but some uniting principles can be identified. Both parts argue against inviolable, language-specific constraints in favor of a derivational explanation for the facts at hand. Both parts derive the phenomena at hand using novel acquisitional strategies (\emph{occultation} and \emph{tolerance}, respectively) and independently motivated components of the grammatical architecture (alternation phonology and the elsewhere principle). And the accounts presented in both parts are inspired by concerns for the sparsity of the primary linguistic data.
